Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/normalsandcurvature.tex
fix figs size

\begin{figure}
    \begin{tabular}{|c|c|}
        \hline
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                width=0.4\textwidth,
                xlabel={Gridstep},
                ylabel={RMSE error},
                x dir=reverse,
                legend pos=north east,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
            ]
                \addplot[
                    color=cyan,
                ] coordinates {
                    (0.125,0.0156736)(0.250,0.031503)(0.375,0.0384303)(0.500,0.0441086)(0.625,0.0418896)(0.750,0.0584604)(0.875,0.065503)(1.000,0.0729735)
                };
                \addlegendentry{ellipsoid};
                \addplot[
                    color=red,
                ] coordinates {
                    (0.125,0.0221236)(0.250,0.0317159)(0.375,0.0542242)(0.500,0.0706101)(0.625,0.09481)(0.750,0.134544)(0.875,0.130578)(1.000,0.127371)
                };
                \addlegendentry{goursat};
                \addplot[
                    color=MyGreen,
                ] coordinates {
                    (0.125,0.0203851)(0.250,0.032289)(0.375,0.0353311)(0.500,0.0568694)(0.625,0.0665957)(0.750,0.106711)(0.875,0.0817172)(1.000,0.104688)
                };
                \addlegendentry{rcube}
                \addplot[
                    color=orange,
                ] coordinates {
                    (0.125,0.0106125)(0.250,0.0223176)(0.375,0.032738)(0.500,0.0365776)(0.625,0.0362568)(0.750,0.0181232)(0.875,0.0303189)(1.000,0.0263066)
                };
                \addlegendentry{sphere9}
            \end{axis}
        \end{tikzpicture} &
        \begin{tikzpicture}
            \centering
            \begin{axis}
                [
                width=0.4\textwidth,
                xlabel={Gridstep},
                ylabel={$E_{\max}$ error},
                x dir=reverse,
                legend pos=north east,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
                ]
                \addplot[
                    color=cyan,
                ] coordinates {
                    (0.125,0.0586128)(0.250,0.0736204)(0.375,0.114564)(0.500,0.114592)(0.625,0.136021)(0.750,0.152418)(0.875,0.139939)(1.000,0.234379)
                };
                \addlegendentry{ellipsoid}
                \addplot[
                    color=red,
                ] coordinates {
                    (0.125,0.0743185)(0.250,0.0810657)(0.375,0.113504)(0.500,0.145859)(0.625,0.256274)(0.750,0.266855)(0.875,0.259101)(1.000,0.274269)
                };
                \addlegendentry{goursat}
                \addplot[
                    color=MyGreen,
                ] coordinates {
                    (0.125,0.0670488)(0.250,0.0926269)(0.375,0.0973621)(0.500,0.137059)(0.625,0.155913)(0.750,0.290065)(0.875,0.164799)(1.000,0.317625)
                };
                \addlegendentry{rcube}
                \addplot[
                    color=orange,
                ] coordinates {
                    (0.125,0.0313599)(0.250,0.044124)(0.375,0.0643389)(0.500,0.0684951)(0.625,0.0853552)(0.750,0.0532733)(0.875,0.064386)(1.000,0.0873334)
                };
                \addlegendentry{sphere9}
            \end{axis}
        \end{tikzpicture} \\
        \hline
    \end{tabular}
    \caption{Error RMSE and $E_{\max}$ as a function of grid resolution}
    \label{fig:errors-normals}
\end{figure}

>>>>

\begin{figure}
    \begin{tabular}{c c}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                width=0.4\textwidth,
                xlabel={Gridstep},
                ylabel={RMSE error},
                x dir=reverse,
                legend pos=north east,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
            ]
                \addplot[
                    color=cyan,
                ] coordinates {
                    (0.125,0.0156736)(0.250,0.031503)(0.375,0.0384303)(0.500,0.0441086)(0.625,0.0418896)(0.750,0.0584604)(0.875,0.065503)(1.000,0.0729735)
                };
                \addlegendentry{ellipsoid};
                \addplot[
                    color=red,
                ] coordinates {
                    (0.125,0.0221236)(0.250,0.0317159)(0.375,0.0542242)(0.500,0.0706101)(0.625,0.09481)(0.750,0.134544)(0.875,0.130578)(1.000,0.127371)
                };
                \addlegendentry{goursat};
                \addplot[
                    color=MyGreen,
                ] coordinates {
                    (0.125,0.0203851)(0.250,0.032289)(0.375,0.0353311)(0.500,0.0568694)(0.625,0.0665957)(0.750,0.106711)(0.875,0.0817172)(1.000,0.104688)
                };
                \addlegendentry{rcube}
                \addplot[
                    color=orange,
                ] coordinates {
                    (0.125,0.0106125)(0.250,0.0223176)(0.375,0.032738)(0.500,0.0365776)(0.625,0.0362568)(0.750,0.0181232)(0.875,0.0303189)(1.000,0.0263066)
                };
                \addlegendentry{sphere9}
            \end{axis}
        \end{tikzpicture} &
        \begin{tikzpicture}
            \centering
            \begin{axis}
                [
                width=0.5\textwidth,
                xlabel={Gridstep},
                ylabel={$E_{\max}$ error},
                x dir=reverse,
                legend pos=north east,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
                ]
                \addplot[
                    color=cyan,
                ] coordinates {
                    (0.125,0.0586128)(0.250,0.0736204)(0.375,0.114564)(0.500,0.114592)(0.625,0.136021)(0.750,0.152418)(0.875,0.139939)(1.000,0.234379)
                };
                \addlegendentry{ellipsoid}
                \addplot[
                    color=red,
                ] coordinates {
                    (0.125,0.0743185)(0.250,0.0810657)(0.375,0.113504)(0.500,0.145859)(0.625,0.256274)(0.750,0.266855)(0.875,0.259101)(1.000,0.274269)
                };
                \addlegendentry{goursat}
                \addplot[
                    color=MyGreen,
                ] coordinates {
                    (0.125,0.0670488)(0.250,0.0926269)(0.375,0.0973621)(0.500,0.137059)(0.625,0.155913)(0.750,0.290065)(0.875,0.164799)(1.000,0.317625)
                };
                \addlegendentry{rcube}
                \addplot[
                    color=orange,
                ] coordinates {
                    (0.125,0.0313599)(0.250,0.044124)(0.375,0.0643389)(0.500,0.0684951)(0.625,0.0853552)(0.750,0.0532733)(0.875,0.064386)(1.000,0.0873334)
                };
                \addlegendentry{sphere9}
            \end{axis}
        \end{tikzpicture} \\
    \end{tabular}
    \caption{Error RMSE and $E_{\max}$ as a function of grid resolution}
    \label{fig:errors-normals}
\end{figure}
